---
title: "30-feature-engineering"
output: html_notebook
---
## Feature Engineering

Catagorize Insulin Level.

First let's try to catagorise the insulin level. If the insulin injected is above 166 then it is abnormal.

```{r cat_insulin}
cat2 <- function(x)ifelse(x<166,"Normal","Abnormal")

cat_insulin <- function(df)
{df%>% 
  mutate_at(c("insulin"),list(insulin_cat=cat2)) 
}


diabetes %>% cat_insulin
```
## Catagorize BMI
Now we categorise BMI.

BMI can be underweight, healthy, overweight and obese accrodin to their respective BMI.




```{r}

cat_bmi <- function(df){
df$bmi %>% cut(breaks=c(0, 18.5, 24.9, 30,Inf), 
                   labels=c("under","Healthy","Over","Obese"))
}
diabetes$bmi_cat <- diabetes %>%cat_bmi
```
## Stadardize Age
Lets's standardize the age. Not having NA would not change anthing as there is no NA in 

```{r standardize}
scale2 <- function(x,na.rm=FALSE )(x-mean(x,na.rm=na.rm))/sd(x,na.rm=na.rm)
std_age <- function(df)
{df%>% 
  mutate_at(c("age"),list(age_std=scale2)) 
}

diabetes %>% std_age()


```

## Detecting Early Marriage

If a woman has 2 or more pregnancy before 23. We can classify it as early marriage.


```{r early_not}

early2 <- function(x)ifelse(x$age<23&x$pregnancies>2,"Early","Not Early")
diabetes$early <- diabetes %>% early2

```

