---
title: "assign4"
output: html_notebook
---
```{r}
library(lubridate)
library(RVerbalExpressions)
```


For the regular expression exercises, try writing first using regular expressions directly, then try using rverbalexpressions. Provide the code for both. 

# Part 1

## R4DS 16.4.5

Create a vector of dates giving the first day of every month in the current year. 
```{r}
`pst <- ydm(today())
pst

first.of.year <- ydm(format(pst, "%Y-01-01"))
first.of.year+month(0:11)
`

```


Write a function that given your birthday (as a date), returns how old you are in years.


```{r}

age_calc <- function(bday) {
  (ymd(bday) %--% today()) %/% years(1)
}
today()
age_calc("1990-8-12")
age_calc(1990-10-12)
```


Write a function that given your birthday, returns the day of the week you were born on. 
```{r}
week_bday <- function(bday){
  weekdays(ymd(bday))
  
}

week_bday("1990-12-8")
```



## R4DS 14.3.2.1

Given the corpus of common words in stringr::words, create regular expressions that find all words that have seven letters or more. (Since this list is long, you might want to use the match argument to str_view() to show only the matching or non-matching words.)


```{r}

 x<- rx() %>% 
  rx_start_of_line() %>% 
  rx_any_of("a-zA-Z") %>% 
  rx_multiple(min = 7) %>% 
  rx_end_of_line() 

str_view(stringr::words, x)

```



```{r}

str_view(stringr::words,".......",match = TRUE)


```


## R4DS 14.3.3.1

Use str_detect to find all words that:

That only contain consonants. (Hint: thinking about matching “not”-vowels.)

```{r}
cons <- rx() %>% 
  rx_start_of_line() %>% 
  rx_anything_but('aeiou') %>% 
  rx_end_of_line()

str_subset(stringr::words,cons)
```



```{r}
str_subset(stringr::words,"^[^aeiou]+$")
```

Empirically verify the rule “i before e except after c”.

```{r}
ier <-  rx() %>% 
  rx_either_of("cei", 
               rx() %>% 
                 rx_something_but("c") %>% 
                 rx_find("ie")
               )
str_subset(stringr::words,ier)
```
These words don't follow the rule



```{r}
str_subset(stringr::words,"ie|[^c]ie")
```


Create a regular expression that will match telephone numbers as commonly written in the US. Split this up into multiple expressions as needed.



```{r}

  
  
tel_num <-   function(number){
  str_view(number,"^\\d{3}[-\\.]\\d{3}[-\\.]\\d{4}$")
}


tel_num(c("217-277-2867", "217.277.2867", "EM7.277.2867"))
```
```{r}
tel_num_rv <- function(number){
telrx <- rx() %>% 
  rx_start_of_line() %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_any_of("-.") %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_any_of("-.") %>%
  rx_digit() %>% 
  rx_repeat_previous(4) %>% 

  rx_end_of_line() %>% 
  grepl(number) %>% 
  print()

}


tel_num_rv(c("217-277-2867", "217.277.2867", "EM7.277.2867"))
```

# Part 2


Choose a dataset (this can be the same dataset as the last assignment, or a new one). Define a predictive modeling problem. Create the appropriate files and notebooks to do the following:

1. Describe the data and the problem

2. Read in and check data

2. Clean up the data. 

*Note: You may request that score for these sections replace your score for the coding portion of Assignment 3.*

4. Using best practices, write four functions which add engineered features to the dataset, including a description and rationale. Include a test to determine whether the features are working as intended. 

5. Prepare the data for modeling

Note: this will form the basis for your midterm project. Take advantage of TA's and my office hours. We can provide feedback and guidance. 

